---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# `r emo::ji("package")` instools -  a collection of functions for health services research

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/INS-Basel/instools/workflows/R-CMD-check/badge.svg)](https://github.com/INS-Basel/instools/actions)
[![R-CMD-check](https://github.com/INS-Basel/instools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/INS-Basel/instools/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of {instools} is to combine and share functions with potential further use 
in one of the research projects at 
the Institute of Nursing Science at the University of Basel.  

Please report any bugs/issues, thanks! 

## Installation

You can install the package from [GitHub](https://github.com/) with:

```{r, eval = F}
# install.packages("remotes")
remotes::install_github("INS-Basel/instools")
``` 


## Types of functions

The package is mostly a collection of self-written utilities. At the moment the  
following groups are included: 

- Functions for reporting: 
  -  Contains 'handy helpers' deemed useful for in parametrized reports 
  (automated reports to generate for e.g. participating organizations) 
  
- Data visualization: 
  - standard color scheme of unibas defined by CI to be accessed as scales for plotting  
  
- Handy helpers: 
  - adding date-column to any dataframe before saving/writing the file  

  
  





